---
title: "Untitled"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
---

library(p8105.datasets)
library(tidyverse)
library(plotly)
knitr::opts_chunk$set(
  fig.width = 8,
  fig.asp=0.7,
  fig.height = 8,
  out.width = '90%'
)
theme_set(theme_minimal())
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

## Problem 1
  This is the link to my website: haoyangyi414.github.io
  
## Problem 2
  Choose NY NOAA datasets to create a flexdashboard.
```{r warning=F}
data("ny_noaa")
noaa_df = ny_noaa %>%
  select(date,id,snow,prcp) %>% # select variables to make plots: snowfall(mm), precipitation (10 mm) and weather station ID
  separate(date,into = c("year","month","day"),sep="-",remove = F) %>% # separate date variable into year, month and day.
  mutate(year = as.numeric(year), month = as.numeric(month),day = as.numeric(day), prcp = prcp/10,
           snow = as.integer(snow)) %>%  # convert type of variables,change unit of prcp
  filter(year == 2010) %>% # use filter to get data in 2010
  select(-date) %>%
  drop_na(snow,prcp)

```
Column {data-width=650}
-----------------------------------------------------------------------

### Chart A

```{r}

```

Column {data-width=350}
-----------------------------------------------------------------------

### Chart B

```{r}

```

### Chart C

```{r}

```

